TestEvol: A Tool for Analyzing Test-Suite Evolution

### 2012-11-02 icse2013demo-testevol/paper.tex
Revised intro

To the best of our knowledge, to date there are no studies in the
literature that investigate how unit test suites evolve. To address
this issue, we defined a technique~\cite{pinto12} that combines
various static- and dynamic-analysis techniques to compute the
differences between the test suites associated with two versions of a
program and categorize such changes along two dimensions: the static
differences between the tests in the two test suites and the
behavioral differences between such tests.

We implemented our technique in a tool, \tool, which enables a
systematic study of test-suite evolution. \tool\ targets Java programs
and JUnit test suites, as Java is a widely used language and JUnit is
the de-facto standard unit-testing framework for Java.  Given two
versions of a program and its test suite, \tool\ automatically
computes differences in the behavior of the test suites on the two
program versions, classifies the actual repairs performed between the
versions, and computes the coverage attained by the tests on the two
program versions.

In this demo, we present \tool, its features and technical details,
and show how it can be used to study how test suites evolved over the
years for a project.  To do so, we will show examples of application
of the tool to a set of real-world open-source software systems.
Specifically, we will show how to use \tool\ to investigate relevant
questions on test evolution, such as: What types of test-suite changes
occur in practice and with what frequency? How often do test repairs
require complex modifications of the tests? Why are tests deleted and
added? Overall, we will show how \tool\ is a useful tool not only for
researchers in the area of test repair (and test evolution in
general), but also to developers and testers who want to better
understand their software systems.

\todo{Discuss \tool's availability at
  \url{http://cheetah.cc.gt.atl.ga.us:8081/testevol/}}.

>>>>

More generally, the ability to analyze how test suites evolve can be
beneficial for developers, as it can help them better understand the
cost and tradeoffs of test evolution. Similarly, project managers can
use information about test-suite evolution to get insight into the
test maintenance process (\eg how often tests are deleted and cause
oss of coverage, how often tests must be adapted because of changes in
the system's API) and ultimately improve it.

Until recently there were no empirical studies in the literature that
investigated how unit test suites evolve and tools that could support
such studies. To address this issue, we defined a technique that
combines various static- and dynamic-analysis techniques to compute
the differences between the test suites associated with two versions
of a program and categorize such changes along two dimensions: the
static differences between the tests in the two test suites and the
behavioral differences between such tests~\cite{pinto12}. Applying our
technique to a number of real-world programs, we were able to discover
several important aspects of test evolution. For example, we found
evidence that, although test repairs are a relatively small fraction
of the activities performed during test evolution, they are indeed
relevant.  We also found that repair techniques that just focus on
oracles (\ie assertions) are likely to be inapplicable in many cases,
that test cases are rarely removed because they are difficult to fix,
but rather because they have become obsolete, and that test cases are
not only added to check bug fixes and test new functionality, as
expected, but also to validate changes in the code.

This demo presents a tool that implements our technique and that we
developed to allow other researchers and practitioners to perform
studies such as we the ones we just summarized. The tool, which is
called \tool, enables a systematic study of test-suite evolution.
Given two versions of a program and corresponding test suites, \tool\
automatically computes differences in the behavior of the test suites
on the two program versions, classifies the actual repairs performed
between the two versions, and computes the coverage attained by the
tests on the versions.

After presenting \tool's features and technical details, the demo
shows how the tool can be used to study how test suites evolved over
the years for a software project.  To do so, we show examples of
application of \tool\ to a set of real-world open-source software
systems.  Specifically, we show how to use \tool\ to investigate
relevant questions on test evolution, such as the following ones: What
types of test-suite changes occur in practice and with what frequency?
How often do test repairs require complex modifications of the tests?
Why are tests deleted and added? Overall, we show how \tool\ is a
useful and practically applicable tool for researchers in the area of
test repair (and test evolution in general), developers and testers
who want to better understand their software maintenance process.
